### 2023-10-11 3.Design/dataset.tex
changed dataset
Reformulated

\subsection{The format}

The values for the data needs to be set not to exceed 1. This is to make sure that the terminal voltage doesn't reach the threshold as explained in \cref{sec:xbarCircuit}.

@@

\begin{figure}[H]
  \centering
  \includesvg[width=\textwidth]{datasets/airline}
  \caption{the airline dataset in a grphic. This is the curve that the regression is trying to reproduce. The vertical lines represent a full year.}
  \label{graph:airline}
\end{figure}

>>>>

To make sure that the terminal voltage doesn't reach the threshold as explained in \cref{sec:xbarCircuit}. The voltage threshold ($V_{threshold}$) was chosen to be $V_{threshold}=0.1V$ because the memristors used in this thesis are purely theorical. The dataset needs to be formated not to exceed this value when converted to voltage (\cref{tab:valConv}), the dataset needs to be trained while not exceeding $1$.

@@

\begin{figure}[H]
  \centering
  \includesvg[width=\textwidth]{datasets/airline}
  \caption{The airline dataset. The vertical lines represent a full year.}
  \label{graph:airline}
\end{figure}
